\documentclass{article}
\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\setlength{\footskip}{5pt}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
\textbf{\Huge \scshape Vinay A} \\ \vspace{1pt}
\small \href{tel:6692881604}{669-288-1604} $|$ \href{mailto:srivinay.appari@sjsu.edu}{\underline{srivinay.appari@sjsu.edu}} $|$ \href{https://linkedin.com/in/SriVinayA/}{\underline{linkedin.com/in/SriVinayA/}} $|$ \href{https://github.com/SriVinayA}{\underline{github.com/SriVinayA}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{San Jose State University}{San Jose, CA}
{Master of Science in Software Engineering}{Aug 2023 – May 2025}
\resumeSubheading
{Sathyabama Institute of Science and Technology}{Chennai, India}
{Bachelor of Engineering in Computer Science}{Aug 2016 – May 2020}
\resumeSubHeadingListEnd



%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Salesforce Developer}{Jan 2023 – Aug 2023}
{Dosti Global}{Hyderabad, India}
\resumeItemListStart
\resumeItem{Designed and developed customized Salesforce solutions using Apex, Visualforce, and Lightning Components to support critical business functions.}
\resumeItem{Integrated Salesforce with external systems using REST/SOAP APIs and middleware, improving data flow efficiency by 25\%.}
\resumeItem{Managed data migration and data quality within Salesforce, ensuring compliance with data governance standards.}
\resumeItem{Developed and executed test plans to ensure the quality and functionality of Salesforce applications, reducing post-deployment issues by 20\%.}
\resumeItem{Collaborated with cross-functional teams to gather requirements and deliver scalable Salesforce solutions, meeting project objectives within 2-week sprint cycles.}
\resumeItemListEnd
\resumeSubheading
{Salesforce Developer}{Sept 2021 – Jan 2023}
{Mastercard (Contract)}{Pune, India}
\resumeItemListStart
\resumeItem{Customized Salesforce applications using Apex and Lightning Web Components (LWC) to enhance user experience and functionality.}
\resumeItem{Integrated Salesforce with financial transaction systems using REST APIs, supporting a 30\% increase in transaction volume.}
\resumeItem{Implemented Salesforce DX and CI/CD tools to streamline deployment processes, reducing release cycles by 15\%.}
\resumeItem{Provided ongoing maintenance and support for Salesforce applications, resolving issues and ensuring 99.9\% system uptime.}
\resumeItem{Created and maintained technical documentation, including design specifications and user guides, to support knowledge sharing.}
\resumeItemListEnd
\resumeSubheading
{Salesforce Developer}{Sept 2020 – Sept 2021}
{Wipro}{Hyderabad, India}
\resumeItemListStart
\resumeItem{Designed and developed Salesforce modules using Apex and Visualforce, improving system performance by 20\%.}
\resumeItem{Collaborated with senior engineers to troubleshoot and resolve technical issues, reducing downtime by 10\%.}
\resumeItem{Participated in code reviews and implemented Salesforce best practices, enhancing coding standards within the team.}
\resumeItem{Gained experience in Salesforce Lightning Experience and multi-tiered system architectures.}
\resumeItem{Assisted in the implementation of Salesforce workflows and process builder to optimize business processes.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Salesforce Community Portal} $|$ \emph{Salesforce Communities, Lightning Web Components, REST APIs}}{}
\resumeItemListStart
\resumeItem{Designed and implemented a Salesforce Community portal to enhance customer engagement and support.}
\resumeItem{Integrated the portal with external systems using REST APIs, improving data accessibility and user experience.}
\resumeItem{Achieved a 30\% increase in customer satisfaction by providing real-time support and self-service options.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{Salesforce Mobile Application} $|$ \emph{Salesforce Mobile, Lightning Components, Apex}}{}
\resumeItemListStart
\resumeItem{Developed a Salesforce mobile application to provide on-the-go access to critical business functions.}
\resumeItem{Customized the application using Lightning Components and Apex, ensuring a seamless user experience.}
\resumeItem{Increased mobile user adoption by 40\% through intuitive design and robust functionality.}
\resumeItemListEnd
\resumeSubHeadingListEnd




%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}: Apex, Java, Python, JavaScript \\
\textbf{Salesforce Technologies}: Visualforce, Lightning Components, Lightning Web Components (LWC), Salesforce APIs \\
\textbf{Integration Tools}: REST/SOAP APIs, Middleware, ETL Tools \\
\textbf{Developer Tools}: Salesforce DX, Git, Jenkins, JIRA \\
\textbf{Core Concepts}: Salesforce Architecture, Data Migration, Data Governance, Agile Methodologies
}}
\end{itemize}



%-------------------------------------------
\end{document}
